Preregistration

### 2021-04-16 manuscript.Rmd
update R + packages

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
  scripts:
    - R/lavaan_helper.R
    - R/simulation.R
    - R/link.R
csl: apa7.csl
numbered_headings: true
bibliography: ["references.bib", "packages.bib"]
---

@@

There are probably few things as frustrating as realizing that the data that you gathered cannot answer the research question you had in mind.
A step to prevent unpleasant surprises is to simulate data.
Simulated data lets you verify that the data you expect to gather and the analysis you plan fit together.
No matter which analytic strategy you plan, it comes with assumptions and a simulation forces you to address these assumptions more directly, than simply thinking about it.
If you identify unrealistic assumptions you can either violate these assumptions and see if the analytic strategy is robust or modify the analytical strategy to address them.
We will show an example using structural equation modeling (SEM) for our Machiavellism example.
However, the general process is applicable to any statistical model, but of course the simulation here is specific to our hypothetical research question.
Of course, one has to make many educated guesses to simulate data that closely matches your expectation.
These guesses strongly depend on the study you are planning, and there cannot be a one fits all solution.
The analytic strategy (i.e. SEM) often gives you a hint about how to simulate data.

If you are unfamiliar with SEM, you may skim over the next sections.
To simulate data for SEM, one has to specify a model and then sample from a multivariate normal distribution following its implied covariance matrix.
The model parameters should mimic the Machiavellism subscale of the short dark triad (SD3).
As a starting point, we can use already published information.
@Jones2013 report loadings seen in Table \@ref(tab:loadings) and report a gender difference (at the manifest level) depending on the sample between `r min(cohend_jones_paulhus)` and `r max(cohend_jones_paulhus)`.

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - git2r
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
  scripts:
    - R/lavaan_helper.R
    - R/simulation.R
    - R/link.R
csl: apa7.csl
numbered_headings: true
bibliography: ["references.bib", "packages.bib"]
---

@@

There are probably few things as frustrating as realizing that the data that you gathered cannot answer the research question you had in mind.
A step to prevent unpleasant surprises is to simulate data.
Simulated data lets you verify that the data you expect to gather and the analysis you plan fit together.
No matter which analytic strategy you plan, it comes with assumptions and a simulation forces you to address these assumptions more directly, than simply thinking about it.
If you identify unrealistic assumptions you can either violate these assumptions and see if the analytic strategy is robust or modify the analytical strategy to address them.
We will show an example using structural equation modeling (SEM) for our Machiavellism example.
However, the general process is applicable to any statistical model, but of course the simulation here is specific to our hypothetical research question.
One has to make many educated guesses to simulate data that closely matches your expectation.
These guesses strongly depend on the study you are planning, and there cannot be a one fits all solution.
The analytic strategy (i.e. SEM) often gives you a hint about how to simulate data.

If you are unfamiliar with SEM, you may skim over the next sections.
To simulate data for SEM, one has to specify a model and then sample from a multivariate normal distribution following its implied covariance matrix.
The model parameters should express out expectations for the Machiavellism subscale of the short dark triad (SD3).
As a starting point, we can use already published information.
@Jones2013 report loadings seen in Table \@ref(tab:loadings) and report a gender difference (at the manifest level) depending on the sample between `r min(cohend_jones_paulhus)` and `r max(cohend_jones_paulhus)`.

### 2021-04-16 preregistration.Rmd
update R + packages

---
title: "Preregistration"
author: "Aaron Peikert"
date: "4/12/2021"
output: html_document
params:
  nsim: 1000
  nmin: 100
  nmax: 1000
  nstep: 100
  seed: 1234
repro:
  packages:
    - tidyverse
    - here
    - lavaan
    - furrr
    - future.batchtools
    - slider
    - patchwork
    - svglite
  scripts:
    - R/simulation.R
---

>>>>

---
title: "Preregistration"
author: "Aaron Peikert"
date: "4/12/2021"
output: html_document
params:
  nsim: 2
  nmin: 100
  nmax: 300
  nstep: 100
  seed: 1234
repro:
  packages:
    - tidyverse
    - here
    - lavaan
    - furrr
    - future.batchtools
    - slider
    - patchwork
    - svglite
  scripts:
    - R/simulation.R
---
